---
title: "Homework 1"
author: "Aaron Mittel"
date: "Authored on 09-21-2022"
output: github_document
---

```{r setup, echo=FALSE, message=FALSE}
data("penguins",package = "palmerpenguins")
library(tidyverse)
```

# Problem 1

The penguins dataset includes location, time, and anatomic features of individual penguins. Notable features of the tabulated data include the following:

* Important variable names include: `r colnames(penguins)`.
* The number of rows is `r nrow(penguins)`.
* The number of columns is `r ncol(penguins)`.
* The mean flipper length, in millimeters, if we ignore missing values is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species)) + geom_point()
ggsave("HW1_Fig_1_scatterplot.pdf", height = 4, width = 6)
```
**Figure 1**: Scatterplot of flipper length (mm) versus bill length (mm). Species is indicated by color (red = Adelie, green = Chinstrap, blue = Gentoo)


# Problem 2

The data frame below is comprised of a random sample of size 10 from a standard normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10 with 3 different factor “levels”.

```{r df_create, echo = FALSE}
set.seed(5)

prob2_df = tibble(
 norm_samp = rnorm(10),
 vec_logical = norm_samp > 0,
 vec_character = character(length = 10),
 vec_factor = factor(c("1","2","3","1","2","3","1","2","3","3"))
)
```

```{r, echo = FALSE}
prob2_df
```

* The mean of the norm_samp variable is `r mean(pull(prob2_df, norm_samp))`.
* The mean of the vec_logical variable is `r mean(pull(prob2_df, vec_logical))`.
* The mean of the vec_character variable is `r mean(pull(prob2_df, vec_character))`.
* The mean of the vec_factor variable is `r mean(pull(prob2_df, vec_factor))`.

The mean is able to be calculated from the norm_samp values and from the logical vector. Taking the mean of the character and factor variables does not work.

However, the code chunk below can be used to coerce non-numeric variables to be treated as an integer (e.g. to convert categorical level to a numeric value) and could then be used  to calculate the mean of the factor variable. This will not affect the already-calculated mean of the norm_samp and logical variables.
```{r, eval = FALSE}
mean(as.numeric(pull(prob2_df, norm_samp)))
mean(as.numeric(pull(prob2_df, vec_logical)))
mean(as.numeric(pull(prob2_df, vec_character)))
mean(as.numeric(pull(prob2_df, vec_factor)))
```

