---
title: "Homework 1"
author: "Aaron Mittel"
date: "Authored on 09-21-2022"
output: github_document
---

```{r, echo=FALSE, message=FALSE}
data("penguins",package = "palmerpenguins")
library(tidyverse)
```

# Problem 1

The penguins dataset includes location, time, and anatomic features of individual penguins. Notable features of the tabulated data include the following:

* Important variable names include: `r colnames(penguins)`.
* The number of rows is `r nrow(penguins)`.
* The number of columns is `r ncol(penguins)`.
* The mean flipper length, in millimeters, if we ignore missing values is `r mean(penguins$flipper_length_mm, na.rm=TRUE)`.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species)) + geom_point()
ggsave("HW1_Fig_1_scatterplot.pdf", height = 4, width = 6)
```
**Figure 1**: Scatterplot of flipper length (mm) versus bill length (mm). Species is indicated by color (red = Adelie, green = Chinstrap, blue = Gentoo)


# Problem 2